The eclipse of ASASSN-21qj

### 2022-09-27 src/tex/ms.tex
[showyourwork] overleaf sync

   \author{M. Kenworthy
          \inst{1}
          \and
          Arttu Sainio
          \inst{2}
          \and
          Eric E. Mamajek
          \inst{3}
          \and
          Joeseph Masiero
          \inst{4}
          \and 
          Amy Mainzer
          \inst{4}
          \and
          Joeseph (Davy) Kirkpatrick
          \inst{4}
          \and 
          Grant M. Kennedy
          \and
          NEOWISE authorship list
          \inst{4}
          \and
          AAVSO observers
          \and
          St\'{e}phane Charbonnel
          \and
        Olivier Garde
        \and
        Pascal Le D\^{u}
        \and
        Lionel Mulato
        \and
        Thomas Petit
          }

   \institute{Leiden Observatory, University of Leiden,
   PO Box 9513, 2300 RA Leiden, The Netherlands\\
   \email{kenworthy@strw.leidenuniv.nl}
         \and
             Arttu's address ...\\
    \and
    JPL
    \and
    Caltech/IPAC, 1200 E California Blvd, Mail Code 100-22, Pasadena, CA 91125, USA
    \and
    NEOWISE
    \and
    AAVSO people
    \and
    XXXX
}
   \date{Received XXXX; accepted XXXX}

@@

>>>>

   \author{M. Kenworthy
          \inst{1}
          \and
          Arttu Sainio
          \inst{2}
          \and
          Eric E. Mamajek
          \inst{3}
          \and
          Joeseph Masiero
          \inst{4}
          \and 
          Amy Mainzer
          \inst{4}
          \and
          Joeseph (Davy) Kirkpatrick
          \inst{4}
          \and 
          Grant M. Kennedy
          \and
          Ludmila Carone
          \and
          NEOWISE authorship list
          \inst{4}
          \and
          AAVSO observers
          \and
          St\'{e}phane Charbonnel
          \and
        Olivier Garde
        \and
        Pascal Le D\^{u}
        \and
        Lionel Mulato
        \and
        Thomas Petit
          }

   \institute{Leiden Observatory, University of Leiden,
   PO Box 9513, 2300 RA Leiden, The Netherlands\\
   \email{kenworthy@strw.leidenuniv.nl}
         \and
             Arttu's address ...\\
    \and
    JPL
    \and
    Caltech/IPAC, 1200 E California Blvd, Mail Code 100-22, Pasadena, CA 91125, USA
    \and
    NEOWISE
    \and
    AAVSO people
    \and
    Space Research Institute, Austrian Academy of Sciences, Schmiedlstrasse 6, A-8042 Graz, Austria
}
   \date{Received XXXX; accepted XXXX}

@@

\begin{figure*}
\begin{centering}
\includegraphics[width=\textwidth]{figures/stellar_lomb_scargle.pdf}
\caption{ASASSN photometry of ASASSN-21qj and the Lomb Scargle periodograms of the photometry in and out of the eclipse.
%
The blue and orange shaded regions in the top panel indicate the range of epochs put into the Lomb Scargle periodogram.
%
Middle panel: The periodograms over a range of 0 to 150 days.
%
Lower panel: The periodogram of the star outside of the eclipse over a range of 0 to 50 days.
}
\label{fig:starlombscargle}
\script{calc_stellar_lomb_scargle.py}
\end{centering}
\end{figure*}
